An umbrella review of the benefits and risks associated with youths' interactions with electronic screens

### 2023-08-14 reports/manuscript.tex
Additional minor editorial changes (#36)
* Add editor changes to manuscript file

* Move included studies into manuscript

* Renumber supp files

* Rerun pipeline

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5300}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and outcomes.
43 effects from 32 meta-analyses met our criteria for statistical certainty.
Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects (range: \emph{r} = -0.14-0.33).
In education, results were mixed; for example, screen use was negatively associated with literacy (\emph{r} = -0.14, 95\% confidence interval {[}CI{]} -0.20 to -0.09, \emph{p} = \textless0.001, \emph{k} = 38, \emph{N} = 18,318), but this effect was positive when parents watched with their children (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
In health, we found evidence for several small negative associations; for example, social media was associated with depression (\emph{r} = 0.12, 95\% CI 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740).
Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\)).
We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
}

@@

While some forms of screen use (e.g., television viewing) may be detrimental to health and wellbeing,\textsuperscript{7,8} evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom™) remains less certain and, in some cases, may even be beneficial.\textsuperscript{9,10}
Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is ``a defining question of our age''.\textsuperscript{11}
With concerns over the impact of screen use including education, health, social development, and psychological well-being, an overview that identifies potential benefits and risks is needed.

Citing the negative effects of screens on health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation\textsuperscript{12} and numerous government agencies\textsuperscript{13,14} and statements by expert groups\textsuperscript{15} have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
They also recommend that children aged 2-5 years should spend no more than one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
However, recent evidence suggests that longer exposures may not have adverse effects on children's behaviour or mental health---and might, in fact, benefit their well-being---as long as exposure does not reach extreme levels (e.g., 7 hours per day)\textsuperscript{16}.
Some research also indicates that content (e.g., video games vs television programs) plays an important role in determining the potential benefit or harm of youths' exposure to screen-based media.\textsuperscript{17}
Indeed, educational screen use is positively related to educational outcomes.\textsuperscript{18}
This evidence has led some researchers to argue that a more nuanced approach to screen use guidelines is required.\textsuperscript{19}

@@

The primary goal of this review was to provide a holistic perspective on the influence of screens on children's lives across a broad range of outcomes.
We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
However, when meta-analyses included a more nuanced examination of exposures, a more complex picture appeared.

@@

Social media was one type of exposure that showed consistent associations with poor health, with no indication of potential benefit.
Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.\textsuperscript{31}
These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression.\textsuperscript{32,33}
Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls.\textsuperscript{34}

@@

\leavevmode\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}%
58. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).
\end{cslreferences}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5312}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and outcomes.
43 effects from 32 meta-analyses met our criteria for statistical certainty.
Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects (range: \emph{r} = -0.14-0.33).
In education, results were mixed; for example, screen use was negatively associated with literacy (\emph{r} = -0.14, 95\% confidence interval {[}CI{]} -0.20 to -0.09, \emph{p} = \textless0.001, \emph{k} = 38, \emph{N} = 18,318), but this effect was positive when parents watched with their children (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
In health, we found evidence for several small negative associations; for example, social media was associated with depression (\emph{r} = 0.12, 95\% CI 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740).
Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\)).
We recommend that caregivers and policymakers carefully weigh the evidence for potential harms and benefits of specific types of screen use.
}

@@

While some forms of screen use (e.g., excessive television viewing) may be detrimental to health and wellbeing,\textsuperscript{7,8} evidence for other forms of screen exposure (e.g., video games or online communication, such as Zoom™) remains less certain and, in some cases, may even be beneficial.\textsuperscript{9,10}
Thus, according to a Nature Human Behaviour editorial, research to determine the effect of screen exposure on youth is ``a defining question of our age''.\textsuperscript{11}
With concerns over the impact of screen use including education, health, social development, and psychological well-being, an overview that identifies potential benefits and risks is needed.

Citing the negative associations between screen use and health (e.g., increased risk of obesity) and health-related behaviours (e.g., sleep), guidelines from the World Health Organisation\textsuperscript{12} and numerous government agencies\textsuperscript{13,14} and statements by expert groups\textsuperscript{15} have recommended that young people's time spent using electronic media devices for entertainment purposes should be limited.
For example, the Australian Government guidelines regarding sedentary behaviour recommend that young children (under the age of two) should not spend any time watching screens.
They also recommend that children aged 2-5 years should spend no more than one hour engaged in recreational sedentary screen use per day, while children aged 5-12 and adolescents should spend no more than two hours.
However, recent evidence suggests that longer exposures may not have adverse effects on children's behaviour or mental health---and might, in fact, benefit their well-being---as long as exposure does not reach extreme levels (e.g., 7 hours per day)\textsuperscript{16}.
Some research also indicates that content (e.g., video games vs television programs) plays an important role in determining the potential benefit or harm of youths' exposure to screen-based media.\textsuperscript{17}
Indeed, educational screen use is positively related to educational outcomes.\textsuperscript{18}
This evidence has led some researchers to argue that a more nuanced approach to screen use guidelines is required.\textsuperscript{19}

@@

The primary goal of this review was to provide a holistic perspective on the association between screen use and a broad range of health- and education-related aspects of children's lives.
We found that when meta-analyses examined general screen use, and did not specify the content, context or device, there was strong evidence showing potentially harmful associations with general learning, literacy, body composition, and depression.
However, when meta-analyses included a more nuanced examination of exposures, a more complex picture appeared.

@@

Social media was one type of exposure that showed consistent---albeit small---associations with poor health, with no indication of potential benefit.
Social media showed strong evidence of harmful associations with risk taking in general, as well as unsafe sex and substance abuse.\textsuperscript{31}
These results align with meta-analytic evidence from adults indicating that social media use is also associated with increased risk of depression.\textsuperscript{32,33}
Recent evidence from social media companies themselves suggest there may also be negative effects of social media on the mental health of young people, especially teenage girls.\textsuperscript{34}

@@

\leavevmode\hypertarget{ref-papadimitriouUmbrellaReviewEvidence2021}{}%
58. Papadimitriou, N. \emph{et al.} An umbrella review of the evidence associating diet and cancer risk at 11 anatomical sites. \emph{Nature Communications} \textbf{12}, 4579 (2021).

\leavevmode\hypertarget{ref-oztopDoesDigitalGeneration2021}{}%
59. Öztop, F. \& Nayci, Ö. Does the Digital Generation Comprehend Better from the Screen or from the Paper?: A Meta-Analysis. \emph{International Online Journal of Education and Teaching} \textbf{8}, 1206--1224 (2021).

\leavevmode\hypertarget{ref-abramiEffectsABRACADABRAReading2015}{}%
60. Abrami, P., Borohkovski, E. \& Lysenko, L. The effects of ABRACADABRA on reading outcomes: A meta-analysis of applied field research. \emph{Journal of Interactive Learning Research} \textbf{26}, 337--367 (2015).

\leavevmode\hypertarget{ref-abramiEffectsABRACADABRAReading2020}{}%
61. Abrami, P. C., Lysenko, L. \& Borokhovski, E. The effects of ABRACADABRA on reading outcomes: An updated meta-analysis and landscape review of applied field research. \emph{Journal of Computer Assisted Learning} \textbf{36}, 260--279 (2020).

\leavevmode\hypertarget{ref-aghasiInternetUseRelation2019}{}%
62. Aghasi, M., Matinfar, A., Golzarand, M., Salari-Moghaddam, A. \& Ebrahimpour-Koujan, S. Internet Use in Relation to Overweight and Obesity: A Systematic Review and Meta-Analysis of Cross-Sectional Studies. \emph{Advances in Nutrition} \textbf{11}, 349--356 (2019).

\leavevmode\hypertarget{ref-alimoradiInternetAddictionSleep2019}{}%
63. Alimoradi, Z. \emph{et al.} Internet addiction and sleep problems: A systematic review and meta-analysis. \emph{Sleep Medicine Reviews} \textbf{47}, 51--61 (2019).

\leavevmode\hypertarget{ref-ameryounImpactGameBasedHealth2018}{}%
64. Ameryoun, A., Sanaeinasab, H., Saffari, M. \& Koenig, H. G. Impact of Game-Based Health Promotion Programs on Body Mass Index in Overweight/Obese Children and Adolescents: A Systematic Review and Meta-Analysis of Randomized Controlled Trials. \emph{Childhood Obesity} \textbf{14}, 67--80 (2018).

\leavevmode\hypertarget{ref-andersonViolentVideoGame2010}{}%
65. Anderson, C. A. \emph{et al.} Violent video game effects on aggression, empathy, and prosocial behavior in Eastern and Western countries: A meta-analytic review. \emph{Psychological Bulletin} \textbf{136}, 151--173 (2010).

\leavevmode\hypertarget{ref-andradePsychologicalEffectsExergames2019}{}%
66. Andrade, A., Correia, C. K. \& Coimbra, D. R. The Psychological Effects of Exergames for Children and Adolescents with Obesity: A Systematic Review and Meta-Analysis. \emph{Cyberpsychology, Behavior, and Social Networking} \textbf{22}, 724--735 (2019).

\leavevmode\hypertarget{ref-arztmannEffectsGamesSTEM2022}{}%
67. Arztmann, M., Hornstra, L., Jeuring, J. \& Kester, L. Effects of games in STEM education: A meta-analysis on the moderating role of student background characteristics. \emph{Studies in Science Education} \textbf{59}, 109--145 (2022).

\leavevmode\hypertarget{ref-aspirantiIPadsTabletsStudents2020}{}%
68. Aspiranti, K. B., Larwin, K. H. \& Schade, B. P. iPads/tablets and students with autism: A meta-analysis of academic effects. \emph{Assistive Technology} \textbf{32}, 23--30 (2020).

\leavevmode\hypertarget{ref-baradaranmahdaviAssociationSedentaryBehavior2021}{}%
69. Baradaran Mahdavi, S., Riahi, R., Vahdatpour, B. \& Kelishadi, R. Association between sedentary behavior and low back pain; A systematic review and meta-analysis. \emph{Health Promotion Perspectives} \textbf{11}, 393--410 (2021).

\leavevmode\hypertarget{ref-barnettActiveVideoGames2011}{}%
70. Barnett, A., Cerin, E. \& Baranowski, T. Active Video Games for Youth: A Systematic Review. \emph{Journal of Physical Activity and Health} \textbf{8}, 724--737 (2011).

\leavevmode\hypertarget{ref-bartelProtectiveRiskFactors2015}{}%
71. Bartel, K. A., Gradisar, M. \& Williamson, P. Protective and risk factors for adolescent sleep: A meta-analytic review. \emph{Sleep Medicine Reviews} \textbf{21}, 72--85 (2015).

\leavevmode\hypertarget{ref-becksilvaEffectsComputerbasedInterventions2022}{}%
72. Beck Silva, K. B., Miranda Pereira, E., Santana, M. L. P. de, Costa, P. R. F. \& Silva, R. de C. R. Effects of computer-based interventions on food consumption and anthropometric parameters of adolescents: A systematic review and metanalysis. \emph{Critical Reviews in Food Science and Nutrition} 1--13 (2022) doi:\href{https://doi.org/10.1080/10408398.2022.2118227}{10.1080/10408398.2022.2118227}.

\leavevmode\hypertarget{ref-benavides-varelaEffectivenessDigitalbasedInterventions2020}{}%
73. Benavides-Varela, S. \emph{et al.} Effectiveness of digital-based interventions for children with mathematical learning difficulties: A meta-analysis. \emph{Computers \& Education} \textbf{157}, 103953 (2020).

\leavevmode\hypertarget{ref-beneriaOnlineInterventionsCannabis2021}{}%
74. Beneria, A. \emph{et al.} Online interventions for cannabis use among adolescents and young adults: Systematic review and meta-analysis. \emph{Early Intervention in Psychiatry} \textbf{16}, 821--844 (2022).

\leavevmode\hypertarget{ref-blokComputerassistedInstructionSupport2002}{}%
75. Blok, H., Oostdam, R., Otter, M. E. \& Overmaat, M. Computer-assisted instruction in support of beginning reading instruction: A review. \emph{Review of Educational Research} \textbf{72}, 101--130 (2002).

\leavevmode\hypertarget{ref-bochnerImpactActiveVideo2015}{}%
76. Bochner, R. E., Sorensen, K. M. \& Belamarich, P. F. The Impact of Active Video Gaming on Weight in Youth: A Meta-Analysis. \emph{Clinical Pediatrics} \textbf{54}, 620--628 (2015).

\leavevmode\hypertarget{ref-bossenEffectivenessSeriousGames2020}{}%
77. Bossen, D. \emph{et al.} Effectiveness of Serious Games to Increase Physical Activity in Children With a Chronic Disease: Systematic Review With Meta-Analysis. \emph{Journal of Medical Internet Research} \textbf{22}, e14549 (2020).

\leavevmode\hypertarget{ref-boylandAdvertisingCueConsume2016}{}%
78. Boyland, E. J. \emph{et al.} Advertising as a cue to consume: A systematic review and meta-analysis of the effects of acute exposure to unhealthy food and nonalcoholic beverage advertising on intake in children and adults. \emph{American Journal of Clinical Nutrition} \textbf{103}, 519--533 (2016).

\leavevmode\hypertarget{ref-boylandAssociationFoodNonalcoholic2022}{}%
79. Boyland, E. \emph{et al.} Association of Food and Nonalcoholic Beverage Marketing With Children and Adolescents' Eating Behaviors and Health: A Systematic Review and Meta-analysis. \emph{JAMA Pediatrics} \textbf{176}, e221037 (2022).

\leavevmode\hypertarget{ref-burkhardtMetaAnalysisLongitudinalAgeDependent2022}{}%
80. Burkhardt, J. \& Lenhard, W. A Meta-Analysis on the Longitudinal, Age-Dependent Effects of Violent Video Games on Aggression. \emph{Media Psychology} \textbf{25}, 499--512 (2022).

\leavevmode\hypertarget{ref-caiAugmentedRealityTechnology2022}{}%
81. Cai, Y., Pan, Z. \& Liu, M. Augmented reality technology in language learning: A meta-analysis. \emph{Journal of Computer Assisted Learning} \textbf{38}, 929--945 (2022).

\leavevmode\hypertarget{ref-caoEffectsModeratorsComputerBased2020}{}%
82. Cao, Y., Huang, T., Huang, J., Xie, X. \& Wang, Y. Effects and Moderators of Computer-Based Training on Children's Executive Functions: A Systematic Review and Meta-Analysis. \emph{Frontiers in Psychology} \textbf{11}, 580329 (2020).

\leavevmode\hypertarget{ref-caoRiskAccidentsChronic2022}{}%
83. Cao, X. \emph{et al.} Risk of Accidents or Chronic Disorders From Improper Use of Mobile Phones: A Systematic Review and Meta-analysis. \emph{Journal of Medical Internet Research} \textbf{24}, e21313 (2022).

\leavevmode\hypertarget{ref-casaleMetaanalysisAssociationSelfesteem2022}{}%
84. Casale, S. \emph{et al.} A meta-analysis on the association between self-esteem and problematic smartphone use. \emph{Computers in Human Behavior} \textbf{134}, 107302 (2022).

\leavevmode\hypertarget{ref-championEffectivenessSchoolbasedEHealth2019}{}%
85. Champion, K. E. \emph{et al.} Effectiveness of school-based eHealth interventions to prevent multiple lifestyle risk behaviours among adolescents: A systematic review and meta-analysis. \emph{The Lancet Digital Health} \textbf{1}, e206--e221 (2019).

\leavevmode\hypertarget{ref-chanDynamicGeometrySoftware2014}{}%
86. Chan, K. K. \& Leung, S. W. Dynamic Geometry Software Improves Mathematical Achievement: Systematic Review and Meta-Analysis. \emph{Journal of Educational Computing Research} \textbf{51}, 311--325 (2014).

\leavevmode\hypertarget{ref-chanImpactESportsOnline2022}{}%
87. Chan, G. \emph{et al.} The impact of eSports and online video gaming on lifestyle behaviours in youth: A systematic review. \emph{Computers in Human Behavior} \textbf{126}, 106974 (2022).

\leavevmode\hypertarget{ref-chenMetaanalysisFactorsPredicting2017}{}%
88. Chen, L., Ho, S. S. \& Lwin, M. O. A meta-analysis of factors predicting cyberbullying perpetration and victimization: From the social cognitive and media effects approach. \emph{New Media \& Society} \textbf{19}, 1194--1213 (2017).

\leavevmode\hypertarget{ref-chenEffectsCompetitionDigital2020}{}%
89. Chen, C.-H., Shih, C.-C. \& Law, V. The Effects of Competition in Digital Game-Based Learning (DGBL): A Meta-Analysis. \emph{Educational Technology Research and Development} \textbf{68}, 1855--1873 (2020).

\leavevmode\hypertarget{ref-cheungHowFeaturesEducational2012}{}%
90. Cheung, A. C. K. \& Slavin, R. E. How features of educational technology applications affect student reading outcomes: A meta-analysis. \emph{Educational Research Review} \textbf{7}, 198--215 (2012).

\leavevmode\hypertarget{ref-cheungEffectivenessEducationalTechnology2013}{}%
91. Cheung, A. C. K. \& Slavin, R. E. The effectiveness of educational technology applications for enhancing mathematics achievement in K-12 classrooms: A meta-analysis. \emph{Educational Research Review} \textbf{9}, 88--113 (2013).

\leavevmode\hypertarget{ref-cheungEffectsEducationalTechnology2013}{}%
92. Cheung, A. C. K. \& Slavin, R. E. Effects of Educational Technology Applications on Reading Outcomes for Struggling Readers: A Best-Evidence Synthesis. \emph{Reading Research Quarterly} \textbf{48}, 277--299 (2013).

\leavevmode\hypertarget{ref-choEffectsUsingMobile2018}{}%
93. Cho, K., Lee, S., Joo, M.-H. \& Becker, B. The Effects of Using Mobile Devices on Student Achievement in Language Learning: A Meta-Analysis. \emph{Education Sciences} \textbf{8}, 105 (2018).

\leavevmode\hypertarget{ref-choduraInterventionsChildrenMathematical2015}{}%
94. Chodura, S., Kuhn, J.-T. \& Holling, H. Interventions for Children With Mathematical Difficulties: A Meta-Analysis. \emph{Zeitschrift für Psychologie} \textbf{223}, 129--144 (2015).

\leavevmode\hypertarget{ref-claussenAllFamilySystematic2022}{}%
95. Claussen, A. H. \emph{et al.} All in the Family? A Systematic Review and Meta-analysis of Parenting and Family Environment as Risk Factors for Attention-Deficit/Hyperactivity Disorder (ADHD) in Children. \emph{Prevention Science} (2022) doi:\href{https://doi.org/10.1007/s11121-022-01358-4}{10.1007/s11121-022-01358-4}.

\leavevmode\hypertarget{ref-clintonReadingPaperCompared2019}{}%
96. Clinton, V. Reading from paper compared to screens: A systematic review and meta-analysis. \emph{Journal of Research in Reading} \textbf{42}, 288--325 (2019).

\leavevmode\hypertarget{ref-comeras-chuecaEffectsActiveVideo2021}{}%
97. Comeras-Chueca, C. \emph{et al.} The Effects of Active Video Games on Health-Related Physical Fitness and Motor Competence in Children and Adolescents with Healthy Weight: A Systematic Review and Meta-Analysis. \emph{International Journal of Environmental Research and Public Health} \textbf{18}, 6965 (2021).

\leavevmode\hypertarget{ref-comeras-chuecaEffectsActiveVideo2021a}{}%
98. Comeras-Chueca, C. \emph{et al.} Effects of Active Video Games on Health-Related Physical Fitness and Motor Competence in Children and Adolescents With Overweight or Obesity: Systematic Review and Meta-Analysis. \emph{JMIR Serious Games} \textbf{9}, e29981 (2021).

\leavevmode\hypertarget{ref-coxAssociationTelevisionViewing2012}{}%
99. Cox, R., Skouteris, H., Rutherford, L. \& Fuller-Tyszkiewicz, M. The Association between Television Viewing and Preschool Child Body Mass Index: A systematic review of English papers published from 1995 to 2010. \emph{Journal of Children and Media} \textbf{6}, 198--220 (2012).

\leavevmode\hypertarget{ref-coyneMetaanalysisProsocialMedia2018}{}%
100. Coyne, S. M. \emph{et al.} A meta-analysis of prosocial media on prosocial behavior, aggression, and empathic concern: A multidimensional approach. \emph{Developmental Psychology} \textbf{54}, 331--347 (2018).

\leavevmode\hypertarget{ref-cunninghamSocialMediaDepression2021}{}%
101. Cunningham, S., Hudson, C. C. \& Harkness, K. Social Media and Depression Symptoms: A Meta-Analysis. \emph{Research on Child and Adolescent Psychopathology} \textbf{49}, 241--253 (2021).

\leavevmode\hypertarget{ref-cushingMetaAnalyticReviewEHealth2010}{}%
102. Cushing, C. C. \& Steele, R. G. A Meta-Analytic Review of eHealth Interventions for Pediatric Health Promoting and Maintaining Behaviors. \emph{Journal of Pediatric Psychology} \textbf{35}, 937--949 (2010).

\leavevmode\hypertarget{ref-darlingSystematicReviewMetaAnalysis2017}{}%
103. Darling, K. E. \& Sato, A. F. Systematic Review and Meta-Analysis Examining the Effectiveness of Mobile Health Technologies in Using Self-Monitoring for Pediatric Weight Management. \emph{Childhood Obesity} \textbf{13}, 347--355 (2017).

\leavevmode\hypertarget{ref-daveyAssessmentSmartphoneAddiction2014}{}%
104. Davey, S. \& Davey, A. Assessment of Smartphone Addiction in Indian Adolescents: A Mixed Method Study by Systematic-review and Meta-analysis Approach. \emph{International Journal of Preventive Medicine} \textbf{5}, 1500--1511 (2014).

\leavevmode\hypertarget{ref-davidHowEffectiveAre2020}{}%
105. David, O. A., Costescu, C., Cardos, R. \& Mogoaşe, C. How Effective are Serious Games for Promoting Mental Health and Health Behavioral Change in Children and Adolescents? A Systematic Review and Meta-analysis. \emph{Child \& Youth Care Forum} \textbf{49}, 817--838 (2020).

\leavevmode\hypertarget{ref-oliveiraPhysicalActivitySedentary2016}{}%
106. Oliveira, R. G. de \& Guedes, D. P. Physical Activity, Sedentary Behavior, Cardiorespiratory Fitness and Metabolic Syndrome in Adolescents: Systematic Review and Meta-Analysis of Observational Evidence. \emph{PLOS ONE} \textbf{11}, e0168503 (2016).

\leavevmode\hypertarget{ref-deriberaCorrelatesYouthViolence2019}{}%
107. de Ribera, O. S., Trajtenberg, N., Shenderovich, Y. \& Murray, J. Correlates of youth violence in low- and middle-income countries: A meta-analysis. \emph{Aggression and Violent Behavior} \textbf{49}, 101306 (2019).

\leavevmode\hypertarget{ref-diMetaanalysisImpactVirtual2022}{}%
108. Di, X. \& Zheng, X. A meta-analysis of the impact of virtual technologies on students' spatial ability. \emph{Educational technology research and development} \textbf{70}, 73--98 (2022).

\leavevmode\hypertarget{ref-eirichAssociationScreenTime2022}{}%
109. Eirich, R. \emph{et al.} Association of Screen Time With Internalizing and Externalizing Behavior Problems in Children 12 Years or Younger: A Systematic Review and Meta-analysis. \emph{JAMA Psychiatry} \textbf{79}, 393 (2022).

\leavevmode\hypertarget{ref-ercelikEffectivenessActiveVideo2022}{}%
110. Erçelik, Z. E. \& Çağlar, S. Effectiveness of active video games in overweight and obese adolescents: A systematic review and meta-analysis of randomized controlled trials. \emph{Annals of Pediatric Endocrinology \& Metabolism} \textbf{27}, 98--104 (2022).

\leavevmode\hypertarget{ref-fangScreenTimeChildhood2019}{}%
111. Fang, K., Mu, M., Liu, K. \& He, Y. Screen time and childhood overweight/obesity: A systematic review and meta-analysis. \emph{Child: Care, Health and Development} \textbf{45}, 744--753 (2019).

\leavevmode\hypertarget{ref-fedeleMobileHealthInterventions2017}{}%
112. Fedele, D. A., Cushing, C. C., Fritz, A., Amaro, C. M. \& Ortega, A. Mobile Health Interventions for Improving Health Outcomes in Youth: A Meta-analysis. \emph{JAMA Pediatrics} \textbf{171}, 461 (2017).

\leavevmode\hypertarget{ref-fengAssociationsMeeting24hour2021}{}%
113. Feng, J., Zheng, C., Sit, C. H.-P., Reilly, J. J. \& Huang, W. Y. Associations between meeting 24-hour movement guidelines and health in the early years: A systematic review and meta-analysis. \emph{Journal of Sports Sciences} \textbf{39}, 2545--2557 (2021).

\leavevmode\hypertarget{ref-fergusonPublicHealthRisks2009}{}%
114. Ferguson, C. J. \& Kilburn, J. The Public Health Risks of Media Violence: A Meta-Analytic Review. \emph{The Journal of Pediatrics} \textbf{154}, 759--763 (2009).

\leavevmode\hypertarget{ref-fergusonAngryBirdsMake2015}{}%
115. Ferguson, C. J. Do Angry Birds Make for Angry Children? A Meta-Analysis of Video Game Influences on Children's and Adolescents' Aggression, Mental Health, Prosocial Behavior, and Academic Performance. \emph{Perspectives on Psychological Science} \textbf{10}, 646--666 (2015).

\leavevmode\hypertarget{ref-fergusonDoesSexyMedia2017}{}%
116. Ferguson, C. J., Nielsen, R. K. L. \& Markey, P. M. Does Sexy Media Promote Teen Sex? A Meta-Analytic and Methodological Review. \emph{Psychiatric Quarterly} \textbf{88}, 349--358 (2017).

\leavevmode\hypertarget{ref-ferguson13ReasonsWhy2019}{}%
117. Ferguson, C. J. 13 Reasons Why Not: A Methodological and Meta-Analytic Review of Evidence Regarding Suicide Contagion by Fictional Media. \emph{Suicide and Life-Threatening Behavior} \textbf{49}, 1178--1186 (2019).

\leavevmode\hypertarget{ref-fergusonReexaminingFindingsAmerican2020}{}%
118. Ferguson, C. J., Copenhaver, A. \& Markey, P. Reexamining the Findings of the American Psychological Association's 2015 Task Force on Violent Media: A Meta-Analysis. \emph{Perspectives on Psychological Science} \textbf{15}, 1423--1443 (2020).

\leavevmode\hypertarget{ref-fergusonThisMetaanalysisScreen2022}{}%
119. Ferguson, C. J. \emph{et al.} Like this meta-analysis: Screen media and mental health. \emph{Professional Psychology: Research and Practice} \textbf{53}, 205--214 (2022).

\leavevmode\hypertarget{ref-fischerEffectsRiskglorifyingMedia2011}{}%
120. Fischer, P., Greitemeyer, T., Kastenmüller, A., Vogrincic, C. \& Sauer, A. The effects of risk-glorifying media exposure on risk-positive cognitions, emotions, and behaviors: A meta-analytic review. \emph{Psychological Bulletin} \textbf{137}, 367--390 (2011).

\leavevmode\hypertarget{ref-folkvordPersuasiveEffectAdvergames2018}{}%
121. Folkvord, F. \& van `t Riet, J. The persuasive effect of advergames promoting unhealthy foods among children: A meta-analysis. \emph{Appetite} \textbf{129}, 245--251 (2018).

\leavevmode\hypertarget{ref-foremanAssociationDigitalSmart2021}{}%
122. Foreman, J. \emph{et al.} Association between digital smart device use and myopia: A systematic review and meta-analysis. \emph{The Lancet Digital Health} \textbf{3}, e806--e818 (2021).

\leavevmode\hypertarget{ref-fowlerHarnessingTechnologicalSolutions2021}{}%
123. Fowler, L. A. \emph{et al.} Harnessing technological solutions for childhood obesity prevention and treatment: A systematic review and meta-analysis of current applications. \emph{International Journal of Obesity} \textbf{45}, 957--981 (2021).

\leavevmode\hypertarget{ref-furenesComparisonChildrenReading2021}{}%
124. Furenes, M. I., Kucirkova, N. \& Bus, A. G. A Comparison of Children's Reading on Paper versus Screen: A Meta-Analysis. \emph{Review of Educational Research} \textbf{91}, 483--517 (2021).

\leavevmode\hypertarget{ref-gaoMetaanalysisActiveVideo2015}{}%
125. Gao, Z., Chen, S., Pasco, D. \& Pope, Z. A meta-analysis of active video games on health outcomes among children and adolescents: A meta-analysis of active video games. \emph{Obesity Reviews} \textbf{16}, 783--794 (2015).

\leavevmode\hypertarget{ref-gardellaSystematicReviewMetaAnalysis2017}{}%
126. Gardella, J. H., Fisher, B. W. \& Teurbe-Tolon, A. R. A Systematic Review and Meta-Analysis of Cyber-Victimization and Educational Outcomes for Adolescents. \emph{Review of Educational Research} \textbf{87}, 283--308 (2017).

\leavevmode\hypertarget{ref-garzonSystematicReviewMetaanalysis2019}{}%
127. Garzón, J., Pavón, J. \& Baldiris, S. Systematic review and meta-analysis of augmented reality in educational settings. \emph{Virtual Reality} \textbf{23}, 447--459 (2019).

\leavevmode\hypertarget{ref-garzonMetaanalysisImpactAugmented2019}{}%
128. Garzón, J. \& Acevedo, J. Meta-analysis of the impact of Augmented Reality on students' learning gains. \emph{Educational Research Review} \textbf{27}, 244--260 (2019).

\leavevmode\hypertarget{ref-ghobadiAssociationEatingTelevision2018}{}%
129. Ghobadi, S. \emph{et al.} Association of eating while television viewing and overweight/obesity among children and adolescents: A systematic review and meta-analysis of observational studies: Television viewing, overweight, obesity, children. \emph{Obesity Reviews} \textbf{19}, 313--320 (2018).

\leavevmode\hypertarget{ref-grabeRoleMediaBody2008}{}%
130. Grabe, S., Ward, L. M. \& Hyde, J. S. The role of the media in body image concerns among women: A meta-analysis of experimental and correlational studies. \emph{Psychological Bulletin} \textbf{134}, 460--476 (2008).

\leavevmode\hypertarget{ref-grahamFormativeAssessmentWriting2015}{}%
131. Graham, S., Hebert, M. \& Harris, K. R. Formative Assessment and Writing: A Meta-Analysis. \emph{The Elementary School Journal} \textbf{115}, 523--547 (2015).

\leavevmode\hypertarget{ref-haoTechnologyAssistedVocabularyLearning2021}{}%
132. Hao, T., Wang, Z. \& Ardasheva, Y. Technology-Assisted Vocabulary Learning for EFL Learners: A Meta-Analysis. \emph{Journal of Research on Educational Effectiveness} \textbf{14}, 645--667 (2021).

\leavevmode\hypertarget{ref-mahdiEffectivenessComputerAssisted2019}{}%
133. Mahdi, H. S. \& Al Khateeb, A. A. The effectiveness of computer-assisted pronunciation training: A meta-analysis. \emph{Review of Education} \textbf{7}, 733--753 (2019).

\leavevmode\hypertarget{ref-heEffectsSmartphoneBasedInterventions2021}{}%
134. He, Z. \emph{et al.} Effects of Smartphone-Based Interventions on Physical Activity in Children and Adolescents: Systematic Review and Meta-analysis. \emph{JMIR mHealth and uHealth} \textbf{9}, e22601 (2021).

\leavevmode\hypertarget{ref-hernandez-jimenezImpactActiveVideo2019}{}%
135. Hernández-Jiménez, C. \emph{et al.} Impact of Active Video Games on Body Mass Index in Children and Adolescents: Systematic Review and Meta-Analysis Evaluating the Quality of Primary Studies. \emph{International Journal of Environmental Research and Public Health} \textbf{16}, 2424 (2019).
